---
title: "Data-types for spIBDerverse functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data-types for spIBDerverse functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spIBDerverse)
library(igraph)
library(sf)
```

In the `spIBDerverse` package, we have two structures that are used by most of the functions, and hence by the `spibder_app()` which gives the shiny GUI. 

The most common object and the primary one for the shiny app is an `igraph` object. This is the primary data structure used by the `igraph` object. @lst-igraph loads an example network and shows it structure. 

Notice that to ensure that we do not have clashes if a user has already add centrality measures, we often also add them using the function `add_centrality_measures()` which adds the common centrality measures to the igraph object but with names like `.degree`, the use of a prefix of `.` should hopefully stop any clashes. 

```{r}
#| lst-cap: Example graph
#| lst-label: lst-igraph
data(example_network)
example_network
```

If you would like to visualise the network on a map, then a node attibute for longitude and latitude is necessary. 

For some of the plotting functions for networks on maps, we also use a network sf object. @lst-sf illustrates this object. We see that is is list that contains two objects both of `sf` types, a node object that contains information about the node positions represented as points, and an edge object that contains the information for the edges represented as linestring objects. 

```{r}
#| lst-cap: Example network sf object
#| lst-label: lst-sf
data(example_sf)
example_sf
```

A network sf object can be obtained from an igraph object as illustrated in @lst-create. 


```{r}
#| lst-cap: Creating an network sf object
#| lst-label: lst-create
example_sf <- convert_sf(
  example_network,
  "lat",
  "long",
  landscape = TRUE
)
```

The package `spIBDerverse` has the following example networks built-in:

- `example_network`, 
- `example_network_2`, 
- `example_network_3`, 
- `example_sf`, and
- `dist_network`. 
