---
title: "Loading data into SpIBDerverse app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading data into SpIBDerverse app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#| message: false
library(spIBDerverse)
library(igraph)
```

In the spIBDerverse app, there are three ways to get data into the app.

# Load examples
Built into the `spIBDerverse` package are numerous example neworks that can be loaded into the app using the `load_examples()` function. 

```{r}
example <- load_example()
example
```

It will return a message if you ask for a dataset that does not exist. 

```{r}
load_example("bob")
```

# Load an IBD network
This will use two files:

- an IBD file which gives the edges, and 
- an META file which has node information:

```{r}
ibd_file <- fs::path_package(
  "extdata/example-ibd-data.tsv",
  package = "spIBDerverse"
)
ibd_file |> readr::read_tsv() |> dplyr::slice(1:5)
```

```{r}
meta_file <- fs::path_package(
  "extdata/example-meta-data.tsv",
  package = "spIBDerverse"
)
meta_file |> readr::read_tsv() |> dplyr::slice(1:5)
```

The IBD file must have two columns `iid1` and `iid2` else you can not create the IBD network, while the META file must have a column called `iid`. 

```{r}
load_ibd_network(ibd_file, meta_file)
```

# Load distance network

